Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence and Forensic Workflow

### 2009-03-12 paper/paper.tex
More work on paper.

%\documentclass[10pt,twocolumn]{article}
\documentclass[10pt, conference]{IEEEtran}
%\IEEEoverridecommandlockouts
%\documentclass{article}
%\documentclass[12pt]{IEEEtran}
%\documentclass{elsart5p}

@@

\item \emph{An Evidence Volume} is a type of AFF Object which is
responsible for providing storage to AFF segments. Volumes may be
implemented in a number of ways, but must provide a mechanism for
storing and retrieving segments by their URN. We discuss several
Volume implementations below.

@@

\item \emph{A stream} is an AFF Object which provides the ability to
seek and read random data. Stream objects are free to implement their storage
in a number of ways, but must provide clients the stream like
interface. We discuss a number of stream types below.

@@

\subsection{ZIP64}
For AFF4, we have changed AFF1's original container file format to
ZIP64\cite{zipspecs}. There are many reasons for this decision:

\begin{itemize}
\item There is already wide support for the ZIP and ZIP64 formats. By
  migrating to these formats, we can take advantage of the rich number
  of user and developer tools already available.
\item ZIP64 includes a CRC32 and timestamp for each segment. We
  believe that the additional integrity checks and timestamps will be
  useful in a forensic environment.
\item ZIP64 already includes support for the ``table of contents''
  envisioned but never implemented by Garfinkel; ZIP64 calls this
  table the ``Central Directory.'' It is written at the end of the
  ZIP64 volume.
\end{itemize}

@@

\begin{figure}
\begin{Verbatim}[frame=single]
stream_period=393216
target_period=196608

0,0,1
65536,0,0
131072,65536,2
196608,65536,1
262144,131072,0
327680,131072,2
\end{Verbatim}
\caption{A Map stream that corresponds to a 3 disk RAID-5 array}\label{ref}
\end{figure}

@@

\subsubsection{Rapidly converting a set of DD images}
Many hardware devices are available to acquire hard disks in the
fields. These often produce a set of uncompressed images split at a
certain size. If the images are split at exactly the same size its
possible to create a FIF archive consisting of a single Overlay
Stream, with a chunk\_size set to the size of each of the images. The
images can then be listed in order as external targets (e.g. {\em
target=file://disk1.dd}). This overlay can be created instantly
without needing to re-compress any of the images. In addition, digital
signatures can be generated for the whole stream or for each segment.

>>>>

%\documentclass[10pt,twocolumn]{article}
\documentclass[10pt, conference]{IEEEtran}
%\IEEEoverridecommandlockouts
%\documentclass{article}
%\documentclass[12pt]{IEEEtran}
%\documentclass{elsart5p}
\usepackage{listings}
\lstset{language=Python,
	frame=single,
	captionpos=b,
	frameround=tttt,
	basicstyle=\small,          % print whole listing small
	keywordstyle=\color{black}\bfseries,
                            % underlined bold black keywords
	identifierstyle=,           % nothing happens
	commentstyle=\color{white}, % white comments
	stringstyle=\ttfamily,      % typewriter type for strings
	showstringspaces=false}     % no special string spaces

@@

\item \emph{An Evidence Volume} is a type of AFF Object which is
responsible for providing storage to AFF segments. Volumes must
provide a mechanism for storing and retrieving segments by their
URN. We discuss two volume implementations below, namely the {\em
Zip64 based volume} and the {\em Directory} based volume.

@@

\item \emph{A stream} is an AFF Object which provides the ability to
seek and read random data. Stream objects implement abstracted
storage, but must provide clients the stream like interface. For
example, we discuss the {\em Image stream} used to store large images,
the {\em Map stream} used to create transformations and the {\em
Encrypted stream} used to provide encryption.

@@

\subsection{ZIP64}
As described above, AFF4 volumes are only required to store and
retrieve segments by their URN. For AFF4, we have changed the default
volume container file format to ZIP64\cite{zipspecs}. There are many
reasons for this decision:

\begin{itemize}
\item There is already wide support for the ZIP and ZIP64 formats. By
  migrating to these formats, we can take advantage of the rich number
  of user and developer tools already available. The volume may be
inspected using any number of commercial zip application (e.g. Windows
Explorer natively supports Zip files).

%% In not sure how this is relevant
%\item ZIP64 includes a CRC32 and timestamp for each segment. We
%  believe that the additional integrity checks and timestamps will be
%  useful in a forensic environment.

\item ZIP64 already includes support for the ``table of contents''
  envisioned but never implemented by Garfinkel; ZIP64 calls this
  table the ``Central Directory.'' It is written at the end of the
  ZIP64 volume.

\item ZIP64 libraries are readily available making proprietary implementations of
interfaces to the AFF4 volume format simple to write. For example a
simple python program to dump out an Image stream is illustrated in
Listing \ref{python_code}.

\begin{lstlisting}[
	float=tb, label=python_code, caption=Sample Python code to
	dump out an Image Stream. As can be seen the chunk index
	segment is used to slice the data segment into chunks. The
	chunks are decompressed and written to the output file.]
volume=zipfile.ZipFile(FILE)
outfd = open("dump.dd","w")
bevy_count = 0

while 1:
    idx_segment = volume.read(STREAM + 
		"%08d.idx" % bevy_count)
    segment = volume.read(STREAM + 
		"%08d" % bevy_count)
    indexes = struct.unpack("<" + "l" * \
	(len(idx_segment)/4),idx_segment)

    for i in range(len(indexes)-1):
	chunk = segment[indexes[i]:
	                indexes[i+1]]
        outfd.write(zlib.decompress(chunk))

    bevy_count += 1
\end{lstlisting}

@@

\begin{lstlisting}[
	float=tb, caption=A Map stream that corresponds to a 3 disk
	RAID-5 array. The targets are URNs for the respective
        disks. Note that map coordinates are given in multiples of 
	block size.,
	label=ref, language=]
aff4:block_size=64k 
aff4:stream_period=6 
aff4:target_period=3

0,0,disk1
1,0,disk0
2,1,disk2
3,1,disk1
4,2,disk0
5,2,disk2
\end{lstlisting}

@@

\subsubsection{Rapidly converting a set of DD images}
Many hardware devices are available to acquire hard disks in the
fields. These often produce a set of uncompressed images split at a
certain size. It is possible to construct a Map Stream which
seamlessly reassembles the logical image from all the individual disk
images. The new stream may be kept in its own volume and may be very
small.

If the images are split at exactly the same size its
possible to create a FIF archive consisting of a single Overlay
Stream, with a chunk\_size set to the size of each of the images. The
images can then be listed in order as external targets (e.g. {\em
target=file://disk1.dd}). This overlay can be created instantly
without needing to re-compress any of the images. In addition, digital
signatures can be generated for the whole stream or for each segment.
